\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-31 Paper/Paper.tex
Write abstract

	TEXT: abstract

@@

	TEXT: conclusion

>>>>

	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), and verify its feasibility. The MAAM uses optical coherence tomography (OCT) and color fundus images to diagnose ocular diseases. It simulates the decision-making process of ophthalmologists by deducing the disease from abnormities. The model is composed of the Abnormity Models, which identify 11 abnormities from OCT images and 8 abnormities from fundus images, and the Diagnosis Model, which diagnoses 12 diseases by integrating information from the Abnormity Models through a fusion mechanism. We also introduce the concept of codominant abnormities and diseases, providing more information for reference. The final model has a diagnosis accuracy of 89\%.

@@

	The main goal of this study is to devise a novel model and verify its feasibility. The MAAM takes both OCT and fundus images as input. We integrate information from different sources by employing the fusion mechanism. Moreover, we use an abnormity-to-disease approach and simulate the decision-making process of ophthalmologists. We also introduced codominant abnormities and diseases, providing more information for reference. There is some room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model, etc.
